Practical consistency management for geographically distributed MMOG servers

### 2011-05-27 trunk/textos/optpaxos/draftv2.tex
propPending

  In this case, when $now > m.ts + w(p)$, $p$ tries to initiate a consensus instance within $G$ to decide $m$. If $p$ cannot start the proposal now, $m$ is enqueued in $propPending$ for being proposed later. Before proposing $m$, $p$ checks whether $m$ -- or a message $m' : m'.ts > m.ts$ -- has already been decided in some previous consensus instance. If it has, $m$ is discarded; otherwise, $p$ starts a consensus instance proposing $m$. Once any message $m$ is decided, if $G \in m.dst$, $m$ is inserted in the $consPending$ list. Besides, $p$ sends a message $\{m, \text{`cons'}\}$ to every $p' : (\exists G' \in m.dst \setminus \{G\}) \wedge (p' \in G')$. When $\{m, \text{`cons'}\}$ is received by each $p' \in G'$, $p'$ checks whether it has ever inserted $m$ in its own $consPending$ list. If not, $p'$ inserts $m$ into $consPending$ and adjusts $barrier(G, G')$ to $m.ts$.

@@

  In this case, when $m$ is optimistically delivered by a process $p$ of group $G$, nothing else is done. The message $m$ should be inserted into the \mbox{\textit{consPending}} list of $p$ only when some message $\{m, \text{`cons'}\}$ is received.
\end{itemize}

>>>>

  In this case, when $now > m.ts + w(p)$, $p$ tries to initiate a consensus instance within $G$ to decide $m$. If $p$ cannot start the proposal now, $m$ is enqueued in $propPending$ for being proposed later. Before proposing $m$, $p$ checks whether $m$ -- or a message $m' : m'.ts > m.ts$ -- has already been decided in some previous consensus instance. If it has, $m$ is discarded; otherwise, $p$ starts a consensus instance proposing $m$. Once any message $m$ is decided, if $G \in m.dst$, $m$ is inserted in the $consPending$ list. Besides, $p$ sends a message $\{m, \text{`cons'}\}$ to every $p' : (\exists G' \in m.dst \setminus \{G\}) \wedge (p' \in G')$. When $\{m, \text{`cons'}\}$ is received by each $p' \in G'$, $p'$ checks whether it has ever inserted $m$ in its own $consPending$ list. If not, $p'$ inserts $m$ into $consPending$ and adjusts $barrier(G, G')$ to $m.ts$. Every message $\{m, \text{`cons'}\}$ is sent through a FIFO channel.

@@

  In this case, when $m$ is optimistically delivered by a process $p$ of group $G$, nothing else is done. The message $m$ is inserted into the \mbox{\textit{consPending}} list of $p$ only $p$ receives some message $\{m, \text{`cons'}\}$.
\end{itemize}
